### 2017-04-06 paper/evaluation.tex
minor change
two paragraphs dimension tradeoffs

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  test suites\Comment{ in open-source projects}?}
\newcommand{\RQB}{How time is distributed across test cases?}
\newcommand{\RQC}{How prevalent is the use of test suite
  parallelization\Comment{ in open-source projects}?}
\newcommand{\RQD}{What are the speedups obtained with parallelization
  (in projects that actually use it) on cost?}
\newcommand{\RQE}{What are the main reasons that prevent developers
  from using test suite parallelization?}
\newcommand{\RQF}{To which extent parallel execution configurations affect testing
  cost and flakiness?}

@@

To answer this research question we surveyed developers involved in a
selection of projects from our benchmark with time-consuming test
suites.  The goal of the survey is to better comprehend developer's
attitude towards the use of parallelism as a mechanism to speedup
regression testing.  We surveyed developers from a total of
\emailsProjects{} projects.  From the initial list of \numMedLong{}
project, we discarded 11 projects that we knew a priori used
parallelization, and \discartedProjects{} projects that we could not find
developer's emails from commit logs.  From this list of projects, we
mined potential participants for our study.  More precisely, we
searched for developer's name and email from the last 20 commits to
the corresponding project repository.  Using this approach, we
identified a total of \emailsSent{} eligible participants.  Finally,
we sent plain-text e-mails to those developers with the survey.  In
total, \emailsAnswered{} developers replied but we discarded
\emailsFalseAnswers{} replies with subjective answers.  Considering
projects covered by the answers, a total of \emailsProjectsAnswered{}
projects (\percEmailsProjectsAnswered{} of the total) were represented
in those replies.  Note that multiple developers on each project
received emails.  We sent the following set of questions to
developers:

@@

To answer this research question we selected projects as follows.  To
avoid noise in our measurements, we first discarded projects
containing failing tests (note that we measure flakiness).  Then, we
sorted projects in descending order of their execution times and
selected the top ten projects from the resulting set.

In this experiment, the baseline technique is \Seq{} and the
evaluation techniques are all the configuration modes listed in
Section~\ref{sec:modes}.  We ran each of the technique for \Fix{X}
times reporting elapsed time and number of failing tests each time.
We reported average results.

@@

Figure~\ref{tab:rq6-efficiency} summarizes our findings.

@@

\Fix{Elaborate results about flakiness}

Figure~\ref{tab:rq6-flaky} summarizes our findings.

>>>>

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  test suites\Comment{ in open-source projects}?}
\newcommand{\RQB}{How time is distributed across test cases?}
\newcommand{\RQC}{How prevalent is the use of test suite
  parallelization\Comment{ in open-source projects}?}
\newcommand{\RQD}{What are the speedups obtained with parallelization
  (in projects that actually use it) on cost?}
\newcommand{\RQE}{What are the main reasons that prevent developers
  from using test suite parallelization?}
\newcommand{\RQF}{To which extent parallel execution configurations affect testing
  costs and flakiness?}

@@

To answer this research question we surveyed developers involved in a
selection of projects from our benchmark with time-consuming test
suites.  The goal of the survey is to better comprehend developer's
attitude towards the use of parallelism as a mechanism to speedup
regression testing.  We surveyed developers from a total of
\emailsProjects{} projects.  From the initial list of \numMedLong{}
project, we discarded 11 projects that we knew a priori used
parallelization, and \discartedProjects{} projects that we could not find
developer's emails from commit logs.  From this list of projects, we
mined potential participants for our study.  More precisely, we
searched for developer's name and email from the last 20 commits to
the corresponding project repository.  Using this approach, we
identified a total of \emailsSent{} eligible participants.  Finally,
we sent plain-text e-mails, containing the survey, to those developers.  In
total, \emailsAnswered{} developers replied but we discarded
\emailsFalseAnswers{} replies with subjective answers.  Considering
projects covered by the answers, a total of \emailsProjectsAnswered{}
projects (\percEmailsProjectsAnswered{} of the total) were represented
in those replies.  Note that multiple developers on each project
received emails.  We sent the following set of questions to
developers:

@@

To answer this research question we selected projects as follows.  To
avoid noise in measuring flakiness we first discarded projects
containing failing tests.  Then, we sorted projects in descending
order of their execution times and selected the top ten projects from
the resulting set.  In this experiment, the baseline technique is
sequential execution (\ie{}, configuration \Seq{}) and the evaluation
techniques consist of all configuration modes listed in
Section~\ref{sec:modes}.  We ran each of those techniques for \Fix{X}
times computing elapsed time and number of failing tests in each run.
Figures~\ref{tab:rq6-efficiency} and~\ref{tab:rq6-flaky} summarize the
results we obtained.

@@

@@
